A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2022-08-19 Analysis/models.Rmd
move files

tibble(Model=c("5-gram","GRNN", "TXL", "GPT-2"), model_str=c(ngram,grnn,txl,gpt),`over 5-gram`=ngram,
             `over GRNN`=grnn,`over TXL`=txl,`over GPT-2`=gpt) %>% 
   mutate(across(`over 5-gram`:`over GPT-2`, ~map2_chr(.x, model_str,do_comparison)),
          `Log Lik`=map_chr(model_str, log_like),
          r_squared=map_chr(model_str, r_squared)) %>% 
   select(-model_str) %>% write_rds(here("Analysis/maze_model_compare.rds")) %>%  knitr::kable()

@@

tibble(Model=c("5-gram","GRNN", "TXL", "GPT-2"), model_str=c(ngram,grnn,txl,gpt),`over 5-gram`=ngram,
             `over GRNN`=grnn,`over TXL`=txl,`over GPT-2`=gpt) %>% 
   mutate(across(`over 5-gram`:`over GPT-2`, ~map2_chr(.x, model_str,do_comparison)),
          `Log Lik`=map_chr(model_str, log_like),
          `r_squared`=map_chr(model_str, r_squared)) %>% 
   select(-model_str)%>% write_rds(here("Analysis/spr_model_compare.rds")) %>% kable()

>>>>

tibble(Model=c("5-gram","GRNN", "TXL", "GPT-2"), model_str=c(ngram,grnn,txl,gpt),`over 5-gram`=ngram,
             `over GRNN`=grnn,`over TXL`=txl,`over GPT-2`=gpt) %>% 
   mutate(across(`over 5-gram`:`over GPT-2`, ~map2_chr(.x, model_str,do_comparison)),
          `Log Lik`=map_chr(model_str, log_like),
          r_squared=map_chr(model_str, r_squared)) %>% 
   select(-model_str) %>% write_rds(here("Analysis/models/maze_model_compare.rds")) %>%  knitr::kable()

@@

tibble(Model=c("5-gram","GRNN", "TXL", "GPT-2"), model_str=c(ngram,grnn,txl,gpt),`over 5-gram`=ngram,
             `over GRNN`=grnn,`over TXL`=txl,`over GPT-2`=gpt) %>% 
   mutate(across(`over 5-gram`:`over GPT-2`, ~map2_chr(.x, model_str,do_comparison)),
          `Log Lik`=map_chr(model_str, log_like),
          `r_squared`=map_chr(model_str, r_squared)) %>% 
   select(-model_str)%>% write_rds(here("Analysis/models/spr_model_compare.rds")) %>% kable()

### 2022-08-19 Papers/Paper/manuscript.Rmd
move files

read_rds(here("Analysis/maze_model_compare.rds")) %>% knitr::kable(format="latex", position="ht",caption="Results of model comparisons on Maze data. Each row shows the additional predictive value gained from adding that model to another model. F values and p values from ANOVA tests between 1-surprisal-source and 2-source models are reported. We also report log likelihoods of models with only one surprisal source and the r-squared correlation between the model's predictions and the data.")

@@

```{r}
maze <- read_rds(here("Analysis/maze_model_compare.rds"))
spr <- read_rds(here("Analysis/spr_model_compare.rds"))
```

@@

read_rds(here("Analysis/spr_model_compare.rds")) %>% knitr::kable(format="latex", position="ht",caption="Results of model comparisons on SPR data. Each row shows the additional predictive value gained from adding that model to another model. F values and p values from ANOVA tests between 1-surprisal-source and 2-source models are reported. We also report log likelihoods of models with only one surprisal source and the r-squared correlation between the model's predictions and the data.")

>>>>

read_rds(here("Analysis/models/maze_model_compare.rds")) %>% knitr::kable(format="latex", position="ht",caption="Results of model comparisons on Maze data. Each row shows the additional predictive value gained from adding that model to another model. F values and p values from ANOVA tests between 1-surprisal-source and 2-source models are reported. We also report log likelihoods of models with only one surprisal source and the r-squared correlation between the model's predictions and the data.")

@@

```{r}
maze <- read_rds(here("Analysis/models/maze_model_compare.rds"))
spr <- read_rds(here("Analysis/models/spr_model_compare.rds"))
```

@@

read_rds(here("Analysis/models/spr_model_compare.rds")) %>% knitr::kable(format="latex", position="ht",caption="Results of model comparisons on SPR data. Each row shows the additional predictive value gained from adding that model to another model. F values and p values from ANOVA tests between 1-surprisal-source and 2-source models are reported. We also report log likelihoods of models with only one surprisal source and the r-squared correlation between the model's predictions and the data.")
